Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-05-02 analyses/reproduce_analyses.Rmd
add full data so I could calculate other sources of larval mortality.

```{r required libraries, results='hide'}
library(MuMIn)      # for standardizing regression coefficients
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(latex2exp)  # using Latex notation for axes labels
library(stringr)
library(MVN)        # assessing multivariate normality assumption
```

@@

gall_selection.df <- read_csv("../data/gall_selection_manuscript_dataset.csv") %>%
  # convert appropriate variables to characters instead of integers
  mutate(Plant_Position = as.character(Plant_Position),
         Gall_Number = as.character(Gall_Number)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%

@@

         # transform and scale traits to approximate multivariate normal assumption
         Diam = chamber.diameter_mm, 
         log.Clutch = log(clutch.size_individuals), 
         sqrt.Pref = sqrt(oviposition.preference_individuals.per.100.shoots),
         # create orthogonal polynomial terms
         sc.Diam.1 = as.numeric(scale(Diam)), #poly(Diam, 2)[ ,1],
         sc.Diam.2 = sc.Diam.1^2, #poly(Diam, 2)[ ,2],
         sc.log.Clutch.1 = as.numeric(scale(log.Clutch)),#poly(log.Clutch, 2)[ ,1],
         sc.log.Clutch.2 = sc.log.Clutch.1^2, #poly(log.Clutch, 2)[ ,2],
         sc.sqrt.Pref.1 = as.numeric(scale(sqrt.Pref)),#poly(sqrt.Pref, 2)[ ,1],
         sc.sqrt.Pref.2 = sc.sqrt.Pref.1^2)#poly(sqrt.Pref, 2)[ ,2])

# scaling before including the model inflates the variance above 1, when everything should be on the same scale
with(gall_selection.df, sd(scale(sc.Diam.1)*scale(sc.log.Clutch.1)))
with(gall_selection.df, sd(scale(sc.Diam.1*sc.log.Clutch.1)))
with(gall_selection.df, sd(scale(sc.Diam.1)*scale(sc.sqrt.Pref.1)))
with(gall_selection.df, sd(scale(sc.Diam.1*sc.sqrt.Pref.1)))
with(gall_selection.df, sd(scale(sc.log.Clutch.1)*scale(sc.sqrt.Pref.1)))
with(gall_selection.df, sd(scale(sc.log.Clutch.1*sc.sqrt.Pref.1)))

# scaling before including the model also can cause deviations from 0, when everything should be zero
with(gall_selection.df, mean(scale(sc.Diam.1)*scale(sc.log.Clutch.1)))
with(gall_selection.df, mean(scale(sc.Diam.1*sc.log.Clutch.1)))
with(gall_selection.df, mean(scale(sc.Diam.1)*scale(sc.sqrt.Pref.1)))
with(gall_selection.df, mean(scale(sc.Diam.1*sc.sqrt.Pref.1)))
with(gall_selection.df, mean(scale(sc.log.Clutch.1)*scale(sc.sqrt.Pref.1)))
with(gall_selection.df, mean(scale(sc.log.Clutch.1*sc.sqrt.Pref.1)))

with(gall_selection.df, cor(sc.sqrt.Pref.1, sc.sqrt.Pref.2))
```

@@

```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam.1, sc.log.Clutch.1, sc.sqrt.Pref.1), univariatePlot = "histogram")
```

```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam.1, sc.log.Clutch.1, sc.sqrt.Pref.1), multivariatePlot = "qq")
```

@@

```{r Food-web contrast model, cache=TRUE}
foodweb_contrast_model <- glmer(
  gall_survival ~ 
    Foodweb*(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb*(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb*(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
summary(foodweb_contrast_model) # Chi-square tests below correspond to Wald z-tests in summary

drop1(foodweb_contrast_model, test="Chisq") # marginal effect of sqrt.Pref^2

# manually testing lower order terms as I've already scaled them to make them mostly orthrogonal
anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.Diam.1), test="Chisq")
anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.log.Clutch.1), test="Chisq") # clear effect
anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.sqrt.Pref.1), test="Chisq")
anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb), test="Chisq") # clear effect

# Revised food-web model after removing non-significant terms
foodweb_model <- glmer(
  gall_survival ~ 
    Foodweb + 
    (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:sc.log.Clutch.1 +
    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb:sc.sqrt.Pref.2 +
    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
summary(foodweb_model)
```

```{r Food-web model, cache=TRUE, eval=FALSE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb:(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

```{r Food-web model old, eval=FALSE}

car::vif(foodweb_model) # GVIF vary between 1.4 and 4, which I don't like

# we get a clear reduction in VIF when we specify a simpler model.
foodweb_contrast_model <- glmer(
  gall_survival ~ 
    Foodweb + (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:sc.log.Clutch.1 +
    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))#,
  #contrast = list(Foodweb = "contr.sum"))
summary(foodweb_contrast_model)
car::vif(foodweb_contrast_model) # after specifying contr.sum, most values are less than 2 (max 2.5)

### THIS APPROACH IS WRONG, IT ALSO STANDARDIZES FITNESS, WHICH IS NOT THE GOAL.
### ONLY THE TRAIT SHOULD BE STANDARDIZED...
### EASIEST WAY TO DO THIS IS TO SCALE BEFORE PUTTING INTO THE MODEL...

# I don't need partial.sd = TRUE, I should actually have it be false...this will be more consistent with the interterpration of intensity of selection. I don't know exactly how the partial changes things...it also may only be relevant when I examine different combinations of predictions through a model selection procedure.
std.coefs <- function(model, partial.sd = FALSE){
  treatments <- fixef(model)[c("FoodwebComplex","FoodwebSimple")]
  temp <- std.coef(model, partial.sd = partial.sd)
  std.coefs <- setNames(c(t(temp[ ,1])), nm = rownames(temp))
  std.coefs[c("FoodwebComplex","FoodwebSimple")] <- treatments # only standardizing trait-fitness relationships, and not main effects of treatment. It doesn't make sense to standardize it as it will alter estimates of mean fitness, which are critical for calculating selection gradients.
  return(std.coefs)
}

std.coef(foodweb_model, partial.sd = FALSE)
cbind(fixef(foodweb_model), std.coefs(foodweb_model))

fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]
std.coefs(foodweb_model)["FoodwebComplex:sc.Diam.1"]
fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]*sd(gall_selection.df$sc.Diam.1)
fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]*sd(filter(gall_selection.df, Foodweb=="Complex")$sc.Diam.1)
```

```{r glmmLasso, eval=FALSE}
library(glmmLasso)
gall_selection.df_test <- gall_selection.df %>%
  mutate(f.Foodweb = factor(Foodweb),
         f.Genotype = factor(Genotype),
         f.Plant_Position = factor(Plant_Position),
         f.Gall_Number = factor(Gall_Number),
         sc.Diam = as.numeric(scale(Diam)),
         sc.log.Clutch = as.numeric(scale(log.Clutch)),
         sc.sqrt.Pref = as.numeric(scale(sqrt.Pref)))

lambda <- seq(500, 0, by=-5)
BIC_vec <- rep(Inf,length(lambda))
AIC_vec <- rep(Inf,length(lambda))

## specify starting values
Delta.start<-as.matrix(t(rep(0, 20+8+111))) # 8+111+613 set intercept, all 19 coefficients, and random effects to starting values of zero
Q.start <- 0.1 #$list(0.1) # diag(c(0.1) using default values from glmmLassoControl

for(i in 1:length(lambda)){
  print(paste("Iteration ", i, sep = ""))

  lasso <- glmmLasso(gall_survival ~ f.Foodweb + 
                       sc.Diam + sc.log.Clutch + sc.sqrt.Pref + 
                       f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
                       I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
                       f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
                       sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
                       f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref,
                     rnd = list(f.Genotype=~1, f.Plant_Position=~1), # , f.Gall_Number=~1
                     family = binomial(link=logit),
                     data = gall_selection.df_test,
                     lambda = lambda[i],
                     switch.NR = F,
                     final.re = TRUE,
                     control = list(start = Delta.start[i, ])) # difficulty providing starting values for random effects, it was easier to use the default.

  print(colnames(lasso$Deltamatrix)[2:20][lasso$Deltamatrix[lasso$conv.step,2:20]!=0])

  BIC_vec[i]<-lasso$bic
  AIC_vec[i]<-lasso$aic

  Delta.start <- rbind(Delta.start, lasso$Deltamatrix[lasso$conv.step, ])

}

plot(AIC_vec ~ lambda)
plot(BIC_vec ~ lambda)

optLassoAIC <- which.min(AIC_vec) # choose whether to optimize with AIC or BIC
optLassoBIC <- which.min(BIC_vec)

# with the full random effect structure, the optimal lambda = 0...
lambda[optLassoAIC]
lambda[optLassoBIC]

# after removing Gall_Number, there is minimal shrinkage for AIC, but substantial shrinkage for BIC
# but how do I decide which method is "best"
lasso_final <- glmmLasso(gall_survival ~ f.Foodweb + 
                       sc.Diam + sc.log.Clutch + sc.sqrt.Pref + 
                       f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
                       I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
                       f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
                       sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
                       f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref,
                     rnd = list(f.Genotype=~1, f.Plant_Position=~1), # , f.Gall_Number=~1
                     family = binomial(link=logit),
                     data = gall_selection.df_test,
                     lambda = lambda[optLassoBIC], # lambda = 43 now, instead of 27...
                     switch.NR = F,
                     final.re = TRUE,
                     control = list(start = Delta.start[optLassoBIC, ]))

summary(lasso_final)

## plot coefficient paths
plot(lambda, Delta.start[2:(length(lambda)+1),2], type="l", lty=1, ylim=c(-0.5,0.5), ylab=expression(hat(beta[i])))
abline(v = lambda[optLasso])
lines(lambda, Delta.start[2:(length(lambda)+1),3], lty=2)
lines(lambda, Delta.start[2:(length(lambda)+1),4], lty=3)
lines(lambda, Delta.start[2:(length(lambda)+1),5], lty=4)
lines(lambda, Delta.start[2:(length(lambda)+1),6], lty=5)
lines(lambda, Delta.start[2:(length(lambda)+1),7], lty=6)
lines(lambda, Delta.start[2:(length(lambda)+1),8], lty=7)
lines(lambda, Delta.start[2:(length(lambda)+1),9], lty=8)
```

```{r test, eval=FALSE}
full_glmer <- glmer(
  gall_survival ~ 
    f.Foodweb + 
    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    f.Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
    f.Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df_test,
  family=binomial(link=logit),
  control=glmerControl(optimizer="bobyqa"))
summary(full_glmer)
drop1(full_glmer, test="Chisq") # no clear evidence of food-web structure altering correlation or quadratic gradients

lin_glmer <- glmer(
  gall_survival ~ 
    f.Foodweb + 
    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df_test,
  family=binomial(link=logit),
  control=glmerControl(optimizer="bobyqa"))
summary(lin_glmer)
drop1(lin_glmer, test="Chisq") # only clear evidence of food-web structure altering selection on clutch size

red_glmer <- glmer(
  gall_survival ~ 
    f.Foodweb + 
    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
    f.Foodweb:sc.log.Clutch +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df_test,
  family=binomial(link=logit),
  control=glmerControl(optimizer="bobyqa"))
summary(red_glmer)

gall_selection.df_test <- gall_selection.df_test %>%
  mutate(c.Diam = Diam - mean(Diam),
         c.log.Clutch = log.Clutch - mean(log.Clutch),
         c.sqrt.Pref = sqrt.Pref - mean(sqrt.Pref))
library(MASS)
red_glmer2 <- glmer(
  gall_survival ~ 
    Foodweb + 
    c.Diam + c.log.Clutch + c.sqrt.Pref +
    I(c.Diam^2) + I(c.log.Clutch^2) + I(c.sqrt.Pref^2) +
    c.Diam:c.log.Clutch + c.Diam:c.sqrt.Pref + c.log.Clutch:c.sqrt.Pref +
    Foodweb:c.log.Clutch +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df_test,
  family=binomial(link=logit),
  control=glmerControl(optimizer="bobyqa"),
  contrast = list(Foodweb="contr.Sum"))
summary(red_glmer2)

red_glmer3 <- glmer(
  gall_survival ~ 
    Foodweb*(scale(poly(Diam, 2)) + scale(poly(log.Clutch, 2)) + scale(poly(sqrt.Pref, 2))) +
    Foodweb*(scale(poly(Diam, 2)[ ,1]):scale(poly(log.Clutch, 2)[ ,1]) + scale(poly(Diam, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1]) + scale(poly(log.Clutch, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1])) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df_test,
  family=binomial(link=logit),
  control=glmerControl(optimizer="bobyqa"))
summary(red_glmer3)

gall_selection.df_test <- gall_selection.df_test %>% mutate(poly.log.Clutch = poly(log.Clutch, 2))

red_glmer4 <- glmer(
  gall_survival ~ 
    Foodweb + (scale(poly(Diam, 2)) + scale(poly(log.Clutch, 2)) + scale(poly(sqrt.Pref, 2))) +
    Foodweb:scale(poly(log.Clutch, 2)[ ,1]) +
    Foodweb + (scale(poly(Diam, 2)[ ,1]):scale(poly(log.Clutch, 2)[ ,1]) + scale(poly(Diam, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1]) + scale(poly(log.Clutch, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1])) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df_test,
  family=binomial(link=logit),
  control=glmerControl(optimizer="bobyqa"))
summary(red_glmer4)

fixef(red_glmer4)
MuMIn::std.coef(red_glmer4, partial.sd = T)
MuMIn::stdizeFit(red_glmer2, data=gall_selection.df_test, scale=T)
fixef(red_glmer2)

# so, with this interpretation, having a significant effect of clutch size will constrain both the slope and curvature of the adaptive landscape more.

# I think I need to rely more on interpreting differences between food-web treatments, rather than getting separate estimates for each food-web treatment, which will have weaker signals. Plus, this will enable me to fill in the covariance matrix...the issue now is, how does the mortality propogate through to affect the selection gradients? 
# the unfortunate thing, is that this may require me to code things a bit differently from the beginning...

test_foodweb_correl <- update(full_glmer, .~. -f.Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref))
summary(test_foodweb_correl)
anova(full_glmer, test_foodweb_correl, test="LR") # no diff, indicates there is no clear effect of food-web on correlational gradients

test_foodweb_quad <- update(full_glmer, .~. -f.Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)))
anova(full_glmer, test_foodweb_quad, test="LR") # no sig. diff, indicates there is no clear effect of food-web on quadratic gradients

test_correl <- update(test_foodweb_correl, .~. -(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref))
anova(test_foodweb_correl, test_correl, test="LR") # sig. diff, argues to keep correlational gradients

test_quad <- update(test_foodweb_quad, .~. -(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)))
anova(test_foodweb_quad, test_quad, test="LR") # sig. diff, argues to keep quadratic gradients

test_foodweb_lin <- glmer(
  gall_survival ~ 
    f.Foodweb + 
    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype) + (1|Plant_Position),
  data = gall_selection.df_test,
  family=binomial(link=logit))

test_lin <- update(test_foodweb_lin, .~. -f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref))
anova(test_foodweb_lin, test_lin, test="LR") # indicates that food-web alters linear selection gradients

test_model <- glmer(
  gall_survival ~ 
    f.Foodweb + 
    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype) + (1|Plant_Position),
  data = gall_selection.df_test,
  family=binomial(link=logit))
summary(test_model)

library(polywog)
test_polywog <- polywog(gall_survival ~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref, 
                        degree = 2,
                        #boot = 100,
                        family="binomial", data=filter(gall_selection.df_test, f.Foodweb=="Complex"))
summary(test_polywog)

library(parcor)

full_glm <- glm(
  gall_survival ~ 
    f.Foodweb + 
    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref),
  data = gall_selection.df_test,
  family=binomial(link=logit),
  na.action = "na.fail") 
```

```{r test model selection, eval=FALSE}
library(MuMIn)

full_glmer <- glmer(
  gall_survival ~ 
    f.Foodweb + 
    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
    f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
    f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df_test,
  family=binomial(link=logit),
  control=glmerControl(optimizer="bobyqa"),
  na.action = "na.fail")
summary(full_glmer)
drop1(full_glmer, test="Chisq") # marginal quadratic effect of Pref. no clear effect of food-web on correlational or quadratic gradients.
drop1(update(full_glmer, .~. -(f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq") # marginal effects of quadratic Diam and Pref and Diam:Clutch
drop1(update(full_glmer, .~. -(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref + f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq") # clear effect of food web on clutch
drop1(update(full_glmer, .~. -(f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref + f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq")

# Set up the cluster
clusterType <- if(length(find.package("snow", quiet = TRUE))) "SOCK" else "PSOCK"
clust <- try(parallel::makeCluster(getOption("cl.cores", 32), type = clusterType))

clusterExport(clust, "gall_selection.df_test")
clusterEvalQ(clust, library(lme4))

# BIC model is VERY restrictive: only foodweb, diam, and pref left everything else exluded in model with lowest BIC
test_dredge <- MuMIn::pdredge(full_glmer, 
                              #fixed = c("f.Foodweb", "sc.Diam", "sc.log.Clutch", "sc.sqrt.Pref", "f.Foodweb:sc.Diam", "f.Foodweb:sc.log.Clutch", "f.Foodweb:sc.sqrt.Pref"), 
                              trace = 2, 
                              rank = "BIC", # AICc # using BIC removes all higher order terms...
                              cluster = clust)

summary(get.models(test_dredge, 1)[[1]])

subset(test_dredge, delta < 10)

test_sub <- MuMIn::model.avg(test_dredge, subset = delta < 10)
test_sub
coefTable(test_sub)
#coefTable(test_dredge)
```

@@

```{r Bootstrap food-web model, cache=TRUE}
boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, #std.coefs, # 
                              nsim=n_boots_analysis, 
                              parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Linear food-web model, cache=TRUE, eval=FALSE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap linear food-web model, cache=TRUE, eval=FALSE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

# Fit linear model with only chamber diameter 
biased_foodweb_model <- glmer(
  gall_survival ~ -1 + Foodweb + 
    Foodweb:sc.Diam.1 + 
    (1|Genotype/Plant_Position/Gall_Number),
  data = biased_foodweb_df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

@@

```{r biased foodweb table, echo=FALSE}
# Print table
biased_foodweb_confint %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term %in% c("FoodwebComplex:sc.Diam.1","FoodwebSimple:sc.Diam.1")) %>%
  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
  #knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
```

@@

```{r Linear egg vs. larval ptoid model, cache=TRUE, eval=FALSE}
linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
```

@@

```{r Get Oviposition preference Fitness Landscape, cache=TRUE, eval=FALSE}

>>>>

```{r required libraries, results='hide'}
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(latex2exp)  # using Latex notation for axes labels
library(stringr)
library(MVN)        # assessing multivariate normality assumption
```

@@

full_df <- read_csv("../data/gall_selection_manuscript_dataset.csv") %>%
  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)), # there were a couple of times where two pupa were found in a single chamber. I set these to 1 to permit an analysis with a binomial model
         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber. I set these to 1 to permit an analysis with a binomial model.
         unknown_mortality = ifelse(rowSums(select(., pupa:early.larval.death)) < 1, 1, 0))

# all sources of mortality
mean(full_df$gall_survival) + mean(full_df$egg.ptoid) + mean(full_df$larval.ptoid) + mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)

mean(full_df$gall_survival) # 40% survival
mean(full_df$egg.ptoid) # 26% egg parasitism
mean(full_df$larval.ptoid) # 11% larval parasitism
mean(full_df$early.larval.death) # 17% early larval death
mean(full_df$unknown_mortality) # 7% unknown

gall_selection.df <- full_df %>%
  # convert appropriate variables to characters instead of integers
  mutate(Plant_Position = as.character(Plant_Position),
         Gall_Number = as.character(Gall_Number)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%

@@

         # transform and scale traits to approximate multivariate normal assumption
         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))

@@

```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
```

```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
```

@@

```{r Food-web model, cache=TRUE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap food-web model, cache=TRUE}
boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Linear food-web model, cache=TRUE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap linear food-web model, cache=TRUE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

# Fit linear model with only chamber diameter 
biased_foodweb_model <- glmer(
  gall_survival ~ -1 + Foodweb + 
    Foodweb:sc.Diam + 
    (1|Genotype/Plant_Position/Gall_Number),
  data = biased_foodweb_df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

@@

```{r biased foodweb table, echo=FALSE}
# Print table
biased_foodweb_confint %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
```

@@

```{r Linear egg vs. larval ptoid model, cache=TRUE}
linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
```

@@

```{r Get Oviposition preference Fitness Landscape, cache=TRUE}
